---
title: "Tidy Tuesday Template"
author: "[Jim Tyhurst, Ph.D.](https://www.jimtyhurst.com/)"
date: "`r Sys.Date()`"
output:
  github_document:
    toc: true
    hard_line_breaks: FALSE
  html_document:
    toc: true
    code_folding: hide
numbersections: true
vignette: >
  %\VignetteIndexEntry{COVID_19_Confirmed_Cases}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Install the needed packages

```{r}
#install.packages("remotes")
#remotes::install_github("thebioengineer/tidytuesdayR")

# Optional package for browsing:
#remotes::install_github("laderast/burro")
```

## Look at the available datasets

```{r}
library(tidytuesdayR)
# This will open up in the help window:
tidytuesdayR::tt_available()
```

## Load the dataset

Load your dataset in with the function below. The input is the date the dataset was issued. You should be able to get this from the `tt_available()` function.

```{r}
# Incoming data comes in as a list
datasets <- tidytuesdayR::tt_load("2020-01-14")
# Show the names of the individual datasets
names(datasets)
dataset <- datasets$passwords
```

To explore the data quickly, use [burro](https://github.com/laderast/burro), which opens a web app for browsing the data:

```{r}
library(burro)
burro::explore_data(dataset,outcome_var = NULL)
```

```{r}
dim(dataset)
```

```{r}
colnames(dataset)
```


## Questions to explore with this data

Given your inital exploration of the data, what was the question you wanted to answer?

## Findings

Put your findings and your visualization code here.

```{r}

```

## Lessons learned

Were there any lessons you learned? Any cool packages you want to talk about?

## References
[Source code](./tidy_tuesday_template.Rmd).

The overall flow of this R markdown file is based on the [template.Rmd](https://github.com/pdxrlang/tidy_tuesday_template/blob/master/template.Rmd) file in the [pdxrlang/tidy_tuesday_template](https://github.com/pdxrlang/tidy_tuesday_template/) project.

Dataset: [College tuition, diversity, and pay](https://github.com/rfordatascience/tidytuesday/tree/master/data/2020/2020-01-14).
