---
title: "Tuition Cost"
author: "[Jim Tyhurst, Ph.D.](https://www.jimtyhurst.com/)"
date: "`r Sys.Date()`"
output:
  github_document:
    toc: true
    hard_line_breaks: FALSE
  html_document:
    toc: true
    code_folding: hide
numbersections: true
vignette: >
  %\VignetteIndexEntry{COVID_19_Confirmed_Cases}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

## TODO

* Read `salary_potential` data.
* Combine `salary_potential` and `tuition_cost` into a single `tbl`.
* Can the `salary_potential` variables `mid_career_pay` and `make_world_better_percent` be predicted from `tuition_cost` variables, such as `type`, `in_state_total`, and `out_of_state_total`?
* Is `salary_potential$stem_percent` correlated with public vs private `type` of school?


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Install the needed packages

```{r install_packages}
#install.packages("remotes")
#remotes::install_github("thebioengineer/tidytuesdayR")

# Optional package for browsing:
#remotes::install_github("laderast/burro")
```

## Look at the available datasets

```{r list_available_datasets}
library(tidytuesdayR)
# This will open up in the help window:
#tidytuesdayR::tt_available()
```

## Load the dataset

Load your dataset in with the function below. The input is the date the dataset was issued. You should be able to get this from the `tt_available()` function.

```{r load_datasets}
# Warning: This takes a long time ...
# Incoming data comes in as a list
datasets <- tidytuesdayR::tt_load('2020-03-10')
# Show the names of the individual datasets
names(datasets)
```

```{r tuition_cost}
df <- datasets$tuition_cost
```

To explore the data quickly, use [burro](https://github.com/laderast/burro), which opens a web app for browsing the data:

```{r browse_tuition_cost}
library(burro)
library(ggplot2)
#burro::explore_data(df,outcome_var = NULL)
```

```{r dim_tuition_cost}
dim(df)
```

```{r colnames_tuition_cost}
colnames(df)
```

```{r univ_name}
head(df$name)
```

```{r state_cols}
library(dplyr)
df %>% 
  dplyr::select(state, state_code, type) %>% 
  head()
```

```{r tuition_cols}
df %>% 
  dplyr::select(
    in_state_tuition, 
    in_state_total, 
    out_of_state_tuition, 
    out_of_state_total
  ) %>% 
  head()
```

## Questions to explore with this data

Given your inital exploration of the data, what was the question you wanted to answer?

## Findings

Put your findings and your visualization code here.

```{r findings}

```

## Lessons learned

Were there any lessons you learned? Any cool packages you want to talk about?

## References
[Source code](./tuition_cost.Rmd).

The overall flow of this R markdown file is based on the [template.Rmd](https://github.com/pdxrlang/tidy_tuesday_template/blob/master/template.Rmd) file in the [pdxrlang/tidy_tuesday_template](https://github.com/pdxrlang/tidy_tuesday_template/) project.

Dataset: [College tuition, diversity, and pay](https://github.com/rfordatascience/tidytuesday/tree/master/data/2020/2020-03-10).
